Experiments with Credit Data

### 2022-08-09 dev/notebooks/real_world.qmd
new and larger synthetic datasets

```{julia}
max_obs = 10000
data_sets = AlgorithmicRecourseDynamics.Data.load_real_world(max_obs)
```

@@

>>>>

```{julia}
max_obs = 1000
data_sets = AlgorithmicRecourseDynamics.Data.load_real_world(max_obs)
```

@@

```{julia}
using Serialization
results = Serialization.deserialize(joinpath(output_path,"results_strict.jls"))
```
